Visually pleasing knot projections

### 2022-06-10 inst/jma_knot.tex
slight rearrangement for issue #64

\begin{description}
\item[{\tt total\_crossing\_potential\_energy()}] The idea is to make
  the crossing points attract one another as if they are
  gravitationally active objects; metric measured by their mutual
  potential energy.  If crossing point $i$ is at position ${\mathbf
    p}_i$ we have $\sum_{i\neq j}\left|{\mathbf p}_i-{\mathbf
    p}_j\right|^{2}$.  The idea is to encourage more compact
  configurations rather than long skinny ones.
\item[{\tt total\_crossing\_angles()}] Here we wish to punish
  configurations with strands that cross at acute angles.  If crossing
  point $i$ has crossing angle $\theta_i$ the metric is
  $\sum_i\left(\cos\theta_i\right)^2$.
\item[{\tt total\_bending\_energy()}] The idea is for the strands to
  preferentially follow elastica curves, as in elementary (nonlinear)
  beam theory.  From differential geometry, the Euler elastica
  potential energy is $\int\kappa(s)^2\,ds$.  In the package, this is
  calculated numerically for each strand and the total returned.
\item[{\tt total\_string\_length()}] The length is just $\int ds$, with a
  nominal value of 5000 (which value is about right for a printed
  copy).
\item[{\tt midpoint\_badness()}] The idea is to suppress strands with
  crossing points too close to the endpoint nodes.  For each crossing
  point $c_ij$ of strand $i$ with strand $j$, we calculate the arc
  length $s=\int_{s=0}^{c_{ij}}\,ds$ from the node to each crossing
  point and normalize with the strand length $\int\,ds$.  We reward
  configurations with normalized crossing point arc lengths that are
  close to $1/2$.  Note that this particular metric is not independent
  of the total crossing potential energy metric.
\item[{\tt node\_crossing\_badness()}] Somewhat complementary to {\em
  total crossing potential energy}, here we make the crossing points
  repel one another, as though they are all charged objects (with the
  same sign).  The idea is to spread out the nodes so no two nodes are
  too close together.  If crossing point $i$ is at position ${\mathbf
    p}_i$ we have $\sum_{i\neq j}\left|{\mathbf p}_i-{\mathbf
    p}_j\right|^{-1}$.
\item[{\tt curvature\_switching\_badness()}] Here the problem is knots
  which should have either all their strands curving to the left, or
  all to the right; the signed curvature should be everywhere the same
  sign (the canonical example would be $8_{18}$ which in earlier
  versions of the software had ugly changes of curvature).  We impose
  a fixed penalty for any knot with more than one sign.
\item[{\tt curvature\_consecutive\_segment\_switching\_badness()}] We
  wish to discourage configurations in which curvature undergoes a
  sudden change at a node.  The value for a single (Bezier) node is
  simply $\left(\delta\kappa\right)^2$, and the penalty for a given
  configuration is the sum of the values for each node.  See
  Figure~\ref{two_trefoil_knots} for motivation and discussion.
\item[{\tt non\_crossing\_strand\_close\_approach\_badness()}] Here
  the idea is to prevent non-intersecting strands from approaching one
  another too closely.  Quite apart from aesthetic considerations,
  this metric prevents the creation of new spurious nodes that would
  disrupt the optimization routines.
\end{description}

>>>>

\begin{description}
\item[{\tt total\_crossing\_potential\_energy()}] The idea is to make
  the crossing points attract one another as if they are
  gravitationally active objects; metric measured by their mutual
  potential energy.  If crossing point $i$ is at position ${\mathbf
    p}_i$ we have $\sum_{i\neq j}\left|{\mathbf p}_i-{\mathbf
    p}_j\right|^{2}$.  The idea is to encourage more compact
  configurations rather than long skinny ones.
\item[{\tt node\_crossing\_badness()}] Here we make the crossing
  points {\em repel} one another, as though they are all charged
  objects (with the same sign).  The idea is to spread out the nodes
  so no two nodes are too close together.  If crossing point $i$ is at
  position ${\mathbf p}_i$ we have $\sum_{i\neq j}\left|{\mathbf
    p}_i-{\mathbf p}_j\right|^{-1}$.  The length scale for this
  repulsion is smaller than that of the attractive term above.  The
  overall potential thus resembles that sometimes seen in atomic
  physics when considering the hydrogen molecule $H_2$: the two
  protons attract one another when distant, but repel when closer.  In
  the package, the intent is for this optimal distance to be a shallow
  minimum and the optimization routine is free to adjust within a wide
  range.
\item[{\tt total\_crossing\_angles()}] Here we wish to punish
  configurations with strands that cross at acute angles.  If crossing
  point $i$ has crossing angle $\theta_i$ the metric is
  $\sum_i\left(\cos\theta_i\right)^2$.
\item[{\tt total\_bending\_energy()}] The idea is for the strands to
  preferentially follow elastica curves, as in elementary (nonlinear)
  beam theory.  From differential geometry, the Euler elastica
  potential energy is $\int\kappa(s)^2\,ds$.  In the package, this is
  calculated numerically for each strand and the total returned.
\item[{\tt total\_string\_length()}] The length is just $\int ds$, with a
  nominal value of 5000 (which value is about right for a printed
  copy).
\item[{\tt midpoint\_badness()}] The idea is to suppress strands with
  crossing points too close to the endpoint nodes.  For each crossing
  point $c_{ij}$ of strand $i$ with strand $j$, we calculate the arc
  length $\int_{s=0}^{c_{ij}}\,ds$ from the node to each crossing
  point and normalize with the strand length $\int\,ds$.  We reward
  configurations with normalized crossing point arc lengths that are
  close to $1/2$.  Note that this particular metric is not independent
  of the total crossing potential energy metric.
\item[{\tt curvature\_switching\_badness()}] Here the problem is knots
  which should have either all their strands curving to the left, or
  all to the right; the signed curvature should be everywhere the same
  sign (the canonical example would be $8_{18}$ which in earlier
  versions of the software had ugly changes of curvature).  We impose
  a fixed penalty for any knot with more than one sign.
\item[{\tt curvature\_consecutive\_segment\_switching\_badness()}] We
  wish to discourage configurations in which curvature undergoes a
  sudden change at a node.  The value for a single (Bezier) node is
  simply $\left(\delta\kappa\right)^2$, and the penalty for a given
  configuration is the sum of the values for each node.  See
  Figure~\ref{two_trefoil_knots} for motivation and discussion.
\item[{\tt non\_crossing\_strand\_close\_approach\_badness()}] Here
  the idea is to prevent non-intersecting strands from approaching one
  another too closely.  Quite apart from aesthetic considerations,
  this metric prevents the creation of new spurious nodes that would
  disrupt the optimization routines.
\end{description}
